{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-03 thesis/thesis.tex
use cleveref

% some useful packages
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdwlist}
\usepackage[numbers,sort]{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
colorlinks=true,
citecolor=citec,
linkcolor=linkc,
urlcolor=urlc,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{microtype}
\usepackage{cleveref}

@@

% % nwf made this but i don't know how to get it to work?
% \usepackage{etoolbox}
% \makeatletter
% \apptocmd{\ref}{%
%   \immediate\write\@auxout%
%     {\expandafter\string\csname nwf@backref\endcsname{#1}{\arabic{page}}}%
% }{}{}
%
% \newcommand{\nwf@backref}[2]{%
%   \ifcsdef{nwf@backrefs@#1}%
%    {\csgappto{nwf@backrefs@#1}{, #2}}%
%    {\csgdef{nwf@backrefs@#1}{#2}}%
% }
% \AtEndDocument{\let\nwf@backref\relax}
%
% \newcommand{\linksto}[1]{\csname nwf@backrefs@#1\endcsname}
% \makeatother

% NB. needs to be defined before mainmatter so they work in hyperref
\definecolor{citec}{RGB}{168,0,84}
\definecolor{linkc}{RGB}{0,84,168}
\definecolor{urlc} {RGB}{168,84,0}

@@

{Many others have collaborated with me directly on the research itself,
whom I thank here in approximate chapter order.
Michael J. Sullivan and Nathaniel Wesley Filardo were Landslide's first users besides myself back in its prototype days.
Joshua Wise, Miriam Zimmerman, and Glenn Willen helped revise my explanation of DPOR in Chapter~\ref{chap:landslide}.
Professor Brandon Lucia provided valuable comments and revisions to Chapter~\ref{chap:quicksand}'s content
that ultimately led to its publication at OOPSLA 2016.
Michael J. Sullivan double-checked the proofs therein.
Professor Timothy Zhu from Penn State University
and Professor Haryadi Gunawi and TA Kevin Zhao from the University of Chicago
graciously allowed me to use their students as guinea pigs
and helped greatly to improve Landslide's stability and robustness for use beyond CMU's walls,
greatly enriching Chapter~\ref{chap:education}'s evaluation.
David Blum and Skye Toor provided
invaluable advice on statistical analysis
that helped me evaluate the student
% justify last line bc of manual page break
\unskip\parfillskip 0pt \par}

@@

\noindent
grade distributions therein.
Mario Dehesa-Azuara generously contributed the
transactional memory data structures
that make up about half of Chapter~\ref{chap:tm}'s evaluation suite.
%
Carlo Angiuli, Evan Cavallo, Ziv Scully, Jim McCann,
Matthew Maurer, Stefan Muller, Guillaume Didier,
Sol Boucher, and Michael J. Sullivan
helped me rehearse and polish the snake fight talk.

>>>>

% some useful packages
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdwlist}
\usepackage[numbers,sort]{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
colorlinks=true,
citecolor=citec,
linkcolor=linkc,
urlcolor=urlc,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{microtype}
\usepackage[nameinlink]{cleveref}

@@

% NB. needs to be defined before mainmatter so they work in hyperref
\definecolor{citec}{RGB}{128,0,64}
\definecolor{linkc}{RGB}{0,64,128}
\definecolor{urlc} {RGB}{128,64,0}

% format section references with no space after the \S
% #1 is the ref number; the #2 and #3 here are the hyperlink boundaries
\crefformat{section}{#2\S{}#1#3}
\Crefformat{section}{#2\S{}#1#3}

@@

{Many others have collaborated with me directly on the research itself,
whom I thank here in approximate chapter order.
Michael J. Sullivan and Nathaniel Wesley Filardo were Landslide's first users besides myself back in its prototype days.
Joshua Wise, Miriam Zimmerman, and Glenn Willen helped revise my explanation of DPOR in \Cref{chap:landslide}.
Professor Brandon Lucia provided valuable comments and revisions to \Cref{chap:quicksand}'s content
that ultimately led to its publication at OOPSLA 2016.
Michael J. Sullivan double-checked the proofs therein.
Professor Timothy Zhu from Penn State University
and Professor Haryadi Gunawi and TA Kevin Zhao from the University of Chicago
graciously allowed me to use their students as guinea pigs
and helped greatly to improve Landslide's stability and robustness for use beyond CMU's walls,
greatly enriching \Cref{chap:education}'s evaluation.
David Blum and Skye Toor provided
invaluable advice on statistical analysis
that helped me evaluate the student
% justify last line bc of manual page break
\unskip\parfillskip 0pt \par}

@@

\noindent
grade distributions therein.
Mario Dehesa-Azuara generously contributed the
transactional memory data structures
that make up about half of \Cref{chap:tm}'s evaluation suite.
%
Carlo Angiuli, Evan Cavallo, Ziv Scully, Jim McCann,
Matthew Maurer, Stefan Muller, Guillaume Didier,
Sol Boucher, and Michael J. Sullivan
helped me rehearse and polish the snake fight talk.
